### 2019-02-19 sections/conclusions.tex
returned future work, and named section "outlook"

\paragraph{Future work}

@@

Additionally, we would like to develop visualisations for \TOPHAT language constructs.
An assistive development environment integrating these visualisations and the presented textual language
would aid domain experts to model workflows in a more accessible manner.
A system that visualizes iTask programs has been developed in the past~\cite{DBLP:conf/sfp/StutterheimPA14}.

>>>>

\subsection{Future work}

@@

Additionally, we would like to develop visualizations for \TOPHAT language constructs.
An assistive development environment integrating these visualizations and the presented textual language
would aid domain experts to model workflows in a more accessible manner.
A system that visualizes iTask programs has been developed in the past~\cite{DBLP:conf/sfp/StutterheimPA14}.
